Individual heterogeneity in the functional topography of the DMN in medial prefrontal cortex 

### 2019-02-08 Manuscript.Rmd
first draft ready!

---
title: 'Individual heterogeneity in the functional topography of the DMN in medial prefrontal cortex '
author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
output:
  word_document: 
    reference_docx: Style_reference.docx
  pdf_document: default
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

## Ideas to do

- The new manuscript organization could go like this: 
1) Meta-analysis and ROIs
2) Summary all
  a) Make sure to report mean density and algebraic connectivity
  b) Cross-method agreement
  c) Spatially averaged community maps reproduce group-level analysis
3) Sliding window
  a) Fiedler vector magnitude as a proxy for affiliation strength
  b) Proportion DMN for mPFC and PCC separately to denote overall stability
  b) Proportion DMN across time-series ~ fiedler vector value (consider renaming propDMN to stability)
4) Threshold the maps and rerun summary all
5) Day 1 vs day 2
6) Session
7) Potential noise
8) Structural correspondence
9) Community > correlation

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlation values with every other vertex), and $W$ is the adjusted correlation matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. This transormation ensures that every row adds up to zero. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975]. Every individual map is therefore binarized by sign in order to evaluate the topography of each sub-network (see next section for details). Figure 1 provides a schematic of the process. Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community to be the one containing the DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects). Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].

@@

For clinical implications, see Hiser & Koenigs 2018. In short, being able to identify functional idiosyncrasies without much data can yield important insights in diagnosis (meh, we always say that..) of a variety of psychological diseases associated with mPFC. It would be more interesting to identify the repercussions to damage in mPFC per individual. They mention that subgenual vmPFC is a common target for deep brain stimulation (or TMS) as a depression treatment. The refinement of the technique is thus coupled to being able to identify personalized functional topologies. They list a number of results related to mPFC functional connectivity too. In the end, their suggestions for clinical implications of mPFC studies rely on the individual measure of functional expanse. (note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas latest)

@@

Mention the lack of interhemispheric distinction, citing Mackey and Petrides in regards to L-R diffs.

It's also worth mentioning that PCC is largely covered by DMN. Then why does this area overlap with SV? I think the Mueller paper mentions that PCC is an important hub of the brain, and perhaps subserves many cognitive functions (recent Wash U paper on this too).

And write a portion on the lack of subcortical reward-related regions (i.e. striatum). Say something like 'incorporating the ventral striatum did notrefine these partitions through either method. This could be due to the lack of signal modulation of this area at rest, and should be examined through behavioral manipulations of value in the future. Instead, here we focus on capturing the intrinsic functional heterogeneity of mPFC as a way to pave the path to refined analyses aimed at disentangling DMN and SV'.

@@

@@

### *Table 1. (UPDATE) Significant brain regions per literature*
| Literature                  | Significant Brain Regions   |
| :-------------------------- | --------------------------: |
| Default Mode Network        | `r paste(dmnLbls)`          |
| Subjective Value            | `r paste(valLbls)`          |

@@

```{r Method (Figure 1), out.width = "100%", fig.align = "center", fig.cap= "Summary of the partitioning scheme and its evaluation. Each connectome if transformed into a normalized Laplacian matrix, whose eigenvector associated with the second-to-lowest eigenvalue assigns negative or positive values to each vertex. These continuous maps are binarized by sign, and compared within and between subjects using the chance-correcting Adjusted Rand Index (ARI)."}
# Change to inflated eventually
include_graphics("./Images/method_figure.png")
```

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Figure 1. Template atlas from Glasser et al. (2016) (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom). Overlapping ROIs (in blue) were defined as the common brain regions that were significantly present in their respective literatures, while a single DMN-specific region (7m, in red) was identified from a permutation analysis comparing these literatures."}
# Change to inflated eventually
include_graphics("./Images/ROIS3.png")
```

```{r Template partition (Fig. 2), out.width="50%", fig.align = "center", fig.cap = "Figure 2. Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}
include_graphics("./Images/FB_FV_example.png")
```

``` {r Partition comparison: all 2 (Fig. 4), fig.align="center", out.width = "40%", fig.cap = "Figure 4. Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. PCC is well aligned across individuals, while mPFC shows clear topographical heterogeneity.", echo=FALSE, message = FALSE}
par(xpd=T)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.1, 
         #cl.lim = c(0,1),
         cl.length = 3,
         #addgrid.col = "grey99",
         cl.pos = "r",
         mar = c(1,1,2,0))
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.cex = 0.1,
         cl.pos = "n",
         #addgrid.col = "grey90",
         mar = c(1,1,2,0), 
         add = T)
segments(0.5,0.5,0.5,100.5, lwd = 2)
segments(0.5,0.5,100.5,0.5, lwd = 2)
segments(0.5,100.5,100.5,100.5, lwd = 2)
segments(100.5,0.5,100.5,100.5, lwd = 2)
mtext(expression(bold("Subject Partitions")), line = 3)
mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Stability per subject: PCC vs mPFC (Fig 10), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 10. ARI between each window and the original pattern for PCC and mPFC separately (left), and the mean per-subject ARI for the whole group (middle). Regardless of the mean ARI, standard deviation remained low for both regions (right).", echo=FALSE, message = FALSE}

@@

``` {r Stability per subject: Fiedler vector vs prop. DMN plot (Fig 11), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 11. Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows. Grey lines denote each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
# Fiedler Vector x proportion of times a vertex was affiliated with DMN
SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
  #geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
  geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 3) +
  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
  scale_y_continuous(limits = c(0,1)) +
  theme_classic()

@@

```{r Thresholded maps (Fig 6), out.width = "100%", fig.align = "center", fig.cap= "Figure 6. A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom). Values that did not meet the threshold were set to zero on the Fiedler vector, and 0.5 on the binarized maps (giving rise to a third community of high-variability vertices). B: Spatial mean of the binarized maps across all participants, indicating the proportion of DMN affiliations per vertex in our sample. This aggregate map shows the common organizational principle of the DMN and non-DMN communities, while also pinpointing the relatively high level of variability in mPFC."}
# Change to inflated eventually
include_graphics("./Images/thresholded.png")
```

``` {r Partition comparison: halves (Fig. 5), fig.align="center", out.width = "60%", fig.cap = "Figure 5. Similarity matrices for 10 example participants showing pattern agreement across days for the whole partition (left), and for PCC and mPFC separately (right). These figures show high agreement within (but not between) subjects, with mPFC again showing significant variability.", echo=FALSE, message = FALSE}
# plots
par(mfrow=c(1,2))
corrplot(RI_all_between_halves_plot, 
         is.corr = F, 
         method = "color",
         addgrid.col = "grey90",
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.1,
         cl.pos = "n",
         #cl.lim = c(0,1),
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1))
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), side = 2, line = 3)
corrplot(RI_PCC_halves_plot, 
         is.corr = F,     
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         #cl.lim = c(0,1),
         cl.pos = "r",
         addgrid.col = "grey90",
         cl.length = 3)
corrplot(RI_PFC_halves_plot, 
         is.corr = F, 
         method = "color",
         type = "upper", 
         tl.pos = "n", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("mPFC")), line = -0.15, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 0.6, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

``` {r Partition comparison: halves ratios (Fig. 6), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 6. mPFC displays higher within-subject agreement than between subjeccts, as evidenced by a high within/between subject mean ARI. PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE}
# plot
ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) + 
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) + 
  ylim(0, 10) +
  geom_hline(yintercept = 1) +
  labs(y = "ARI Ratio", x = "") + 
  theme_classic(base_size = 14)
```

``` {r Partition comparison: session similarity matrices (Fig. 7), fig.align="center", out.width = "60%", fig.cap = "Figure 7. Similarity matrices showing pattern agreement across sessions for the whole partition (left), and for PCC and mPFC separately (right) (10 example subjects). The pattern from the daily analysis is preserved, with marked individuality for mPFC, but not PCC.", echo=FALSE, message = FALSE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess_plot, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(-0.03,1),
         cl.pos = "n",
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1), 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,40.5, lwd = 2)
# segments(0.5,0.5,40.5,0.5, lwd = 2)
# segments(0.5,40.5,40.5,40.5, lwd = 2)
# segments(40.5,0.5,40.5,40.5, lwd = 2)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
corrplot(RI_PCC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "r", 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
corrplot(RI_PFC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("mPFC")), line = 0, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 1, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

``` {r Partition comparison: session ratios (Fig. 8), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 8. Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions. Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE}
ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) + 
  ylim(0, NA) +
  geom_hline(yintercept = 1) +
  labs(y = "ARI Ratio", x = "") + 
  theme_classic(base_size = 14)
```

``` {r Noise Effects: tSNR Comparison (Fig. 12), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 12. Mean tSNR for mPFC and PCC across participants. This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE}
# Plot the mPFC SNR vs PCC SNR for each subject (one figure containing all subjects)
snrmeanComp_plot <- ggplot(data = SNR_meanComp$Values, aes(Region, SNR, fill = Region)) +
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) +
  labs(x = "", y = "tSNR") +
  theme(text = element_text(size=35)) +
  theme_classic()
snrmeanComp_plot
```

``` {r Noise Effects: Mean R-sqd mPFC and PCC (Fig. 13 UPDATE IN TEXT FROM THIS FIG ON), fig.align="center", fig.width=6, fig.height=4, fig.cap = "Figure 13. Differences in mean R-squared values for each region per participant. The figure shows that PCC vertices tend to be more coupled with the overall dynamics of DMN across subjects.", echo=FALSE, message = FALSE}
#v4
```

``` {r Noise Effects: R-sqd vs tSNR (Fig. 14), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Figure 14. Vertex tSNR values across all subjects are correlated with their position along the z-axis in mPFC, with vmPFC showing the lowest tSNR (left). However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE}
# grid.arrange(v6, v7, ncol = 2)
# par(mfrow = c(1,2))
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "R-squared Value",
#               ylab = "Z-Coordinate")
# 
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$varCoeff, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "Coefficient of Variation (SNR)",
#               ylab = "")

@@

``` {r Correlation vs community detection: comparison plot (Fig. 16), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Figure 16. Day 1 vs Day 2 oefficients of spatial correlations for every method, as well as between methods. Community detection through spectral partitioning provides the most stable inter-day estimates, even though both methods show good level of agreement.", echo=FALSE, message = FALSE}
# Day 1 vs Day 2 Spatial Correlation Comparison
prepostComp_plot <- ggplot(data = prepostComp, aes(Approach, Correlation, fill = Approach)) +
  geom_boxplot(show.legend = F) +
  labs(x = "", y = "Correlation Coefficient") +
  ylim(0,1) +
  theme(text = element_text(size=35)) +
  theme_classic()
prepostComp_plot

@@

```{r B&B comparison (Figure 15), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between maps produced by seed-based connectivity based on Braga & Buckner's (2017) criterion, and those produced by spectral partitioning. Networks A and B were produced by carefully selecting a DLPFC seed (pointed by the green arrows). In each case, our DMN and non-DMN networks map remarkably well to their proposed functional organization."}
# Change to inflated eventually
include_graphics("./Images/braga_comparison.png")
```

>>>>

---
title: 'Individual heterogeneity in the functional topography of the DMN in medial prefrontal cortex '
author: "Claudio Toro-Serey, Sean Tobyne, & Joseph T. McGuire"
output:
  pdf_document: default
  word_document: 
    reference_docx: Style_reference.docx
  html_document: default
bibliography: mPFC_paper.bib
header-includes:
    - \usepackage{setspace}\doublespacing
---

@@

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlation values with every other vertex), and $W$ is the adjusted correlation matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. This transormation ensures that every row adds up to zero. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975]. Every individual map is therefore binarized by sign in order to evaluate the topography of each sub-network (see next section for details). Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community to be the one containing the DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects). Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].

@@

For clinical implications, see Hiser & Koenigs 2018. In short, being able to identify functional idiosyncrasies without much data can yield important insights in diagnosis (meh, we always say that..) of a variety of psychological diseases associated with mPFC. It would be more interesting to identify the repercussions of damage in mPFC per individual. They mention that subgenual vmPFC is a common target for deep brain stimulation (or TMS) as a depression treatment. The refinement of the technique is thus coupled to being able to identify personalized functional topologies. They list a number of results related to mPFC functional connectivity too. In the end, their suggestions for clinical implications of mPFC studies rely on the individual measure of functional expanse. (note that social-relevant areas in their meta analysis look similar to our patterns, and the emotion part to Barbas' latest)

@@

@@

Interhemispheric differences? citing Mackey and Petrides

And write a portion on the lack of subcortical reward-related regions (i.e. striatum). Say something like 'incorporating the ventral striatum did not refine these partitions through either method. This could be due to the lack of signal modulation of this area at rest, and should be examined through behavioral manipulations of value in the future. Instead, here we focus on capturing the intrinsic functional heterogeneity of mPFC as a way to pave the path to refined analyses aimed at disentangling DMN and SV'. It is worth noting that the SV-only area from the meta-analysis tends to land in non-DMN, although it ends up in no-ones land when thresholding the maps.

@@

<!--
### *Table 1. (UPDATE) Significant brain regions per literature*
| Literature                  | Significant Brain Regions   |
| :-------------------------- | --------------------------: |
| Default Mode Network        | `r paste(dmnLbls)`          |
| Subjective Value            | `r paste(valLbls)`          |
-->

@@

<!---
```{r Method (Figure 1), out.width = "100%", fig.align = "center", fig.cap= "Summary of the partitioning scheme and its evaluation. Each connectome if transformed into a normalized Laplacian matrix, whose eigenvector associated with the second-to-lowest eigenvalue assigns negative or positive values to each vertex. These continuous maps are binarized by sign, and compared within and between subjects using the chance-correcting Adjusted Rand Index (ARI)."}
# Change to inflated eventually
include_graphics("./Images/method_figure.png")
```
-->

```{r Meta-analysis ROIs (Fig. 1), out.width = "50%", fig.align = "center", fig.cap= "Template atlas from Glasser et al. (2016) (top), as well as the common and unique brain regions associated with DMN and subjective value (bottom). DMN regions defined by Yeo et al. (2011) in blue, which encompass areas of considerable overlap between DMN and SV. Literature-specific regions (7m in yellow and s32 in red) were identified from a permutation analysis comparing these literatures."}
# Change to inflated eventually
include_graphics("./Images/ROIS3.png")
```

```{r Template partition (Fig. 2), out.width="50%", fig.align = "center", fig.cap = "Brain partition for an example subject (100307). Fiedler vector values (top) are mapped onto the brain surface, dividing it into positive and negative communities. The bottom brain shows the binarized Fiedler vector, with yellow areas denoting the DMN community (as indicated by coverage of area 7m)."}
include_graphics("./Images/FB_FV_example.png")
```

``` {r Partition comparison: all 2 (Fig. 4), fig.align="center", out.width = "40%", fig.cap = "Similarity matrix showing ARI values among all subjects for PCC (lower triangle) and mPFC (upper triangle) separately. PCC is better aligned across individuals than mPFC.", echo=FALSE, message = FALSE}
par(xpd=T)
corrplot(RI_PCC,
         is.corr = F, 
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.1, 
         #cl.lim = c(0,1),
         cl.length = 3,
         #addgrid.col = "grey99",
         cl.pos = "r",
         mar = c(1,1,2,0))
corrplot(RI_PFC, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.cex = 0.1,
         cl.pos = "n",
         #addgrid.col = "grey90",
         mar = c(1,1,2,0), 
         add = T)
segments(0.5,0.5,0.5,100.5, lwd = 2)
segments(0.5,0.5,100.5,0.5, lwd = 2)
segments(0.5,100.5,100.5,100.5, lwd = 2)
segments(100.5,0.5,100.5,100.5, lwd = 2)
mtext(expression(bold("Subject Partitions")), line = 3)
mtext(expression(bold("Subject Partitions")), side = 2, line = -0.8)
mtext(expression(bold("mPFC")), line = 2, at = par("usr")[1]+0.73*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 4, at = par("usr")[1]+0.18*diff(par("usr")[1:2]), col = "steelblue4")

@@

``` {r Stability per subject: PCC vs mPFC (Fig 5), fig.align="center", fig.width=5, fig.height=3, fig.cap = "MEan agreement between partitions from each sliding window and the map produced with the whole data per subject, for mPFC and PCC separately (left), and the distribution of standard deviations along the time series per subject (right). There was strong (at least 50% after adjusting for chance) and stable agreement in both regions, but higher for PCC.", echo=FALSE, message = FALSE}

@@

``` {r Stability per subject: Fiedler vector vs prop. DMN plot (Fig 6), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Relationship between the magnitude of Fiedler vector values and the proportion of affiliations of a vertex with DMN throughout 37 sliding windows. Grey lines display each subject's association, while the black line shows the fit from a mixed effects logistic regression.", echo=FALSE, message = FALSE}
# Fiedler Vector x proportion of times a vertex was affiliated with DMN
SC_FVvPDMN_plot <- ggplot(data = allSummaries) +
  geom_smooth(aes(FiedlerVec, slidePropDMN, group = SubjID), color = "gray", fill = "gray", show.legend = F, alpha = 0.3) +
  #geom_line(aes(FiedlerVec, FittedVals), alpha = 1, size = 3) +
  geom_line(data = SC_FVvPDMN_fits, aes(FiedlerVector, Fitted_Proportion), lwd = 3) +
  labs(x = "Fiedler Vector Values", y = "Proportion of DMN Affiliations") +
  scale_y_continuous(limits = c(0,1)) +
  theme_classic()

@@

```{r Thresholded maps (Fig 7), out.width = "100%", fig.align = "center", fig.cap= "A: Thresholded Fiedler vector maps for subject 100307 (top), and its binarized form (bottom). Values that did not meet the threshold were set to zero on the Fiedler vector, and 0.5 on the binarized maps (giving rise to a third community of high-variability vertices). B: Spatial mean of the binarized maps across all participants, indicating the proportion of DMN affiliations per vertex in our sample. This aggregate map shows the common organizational principle of the DMN and non-DMN communities, while also pinpointing the relatively high level of variability in mPFC."}
# Change to inflated eventually
include_graphics("./Images/thresholded.png")
```

``` {r Partition comparison: halves (Fig. 8), fig.align="center", out.width = "60%", fig.cap = "Similarity matrices for 10 example participants showing pattern agreement across days for the whole brain (left), and for PCC and mPFC separately (right). These figures show high agreement within (but not between) subjects, with mPFC again showing higher heterogeneity in the group.", echo=FALSE, message = FALSE}
# plots
par(mfrow=c(1,2))
corrplot(RI_all_between_halves_plot, 
         is.corr = F, 
         method = "color",
         addgrid.col = "grey90",
         tl.pos = "n", 
         tl.col = "black",
         tl.cex = 0.1,
         cl.pos = "n",
         #cl.lim = c(0,1),
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1))
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), side = 2, line = 3)
corrplot(RI_PCC_halves_plot, 
         is.corr = F,     
         method = "color",
         type = "lower", 
         tl.pos = "n", 
         #cl.lim = c(0,1),
         cl.pos = "r",
         addgrid.col = "grey90",
         cl.length = 3)
corrplot(RI_PFC_halves_plot, 
         is.corr = F, 
         method = "color",
         type = "upper", 
         tl.pos = "n", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Day 1 and Day 2)")), line = 1)
mtext(expression(bold("mPFC")), line = -0.15, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 0.6, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

``` {r Partition comparison: halves ratios (Fig. 9), fig.align="center", fig.width=3, fig.height=3, fig.cap = "mPFC yields higher within-subject agreement than between subjects, as evidenced by a high within/between subject mean ARI. PCC also shows some level of topographical idiosyncrasy (ratio > 1), but significantly lower than mPFC.", echo=FALSE, message = FALSE}
# plot
ggplot(data = Halves_RIRatios_summary, aes(Region, RI, fill = Region)) + 
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) + 
  ylim(0, 10) +
  geom_hline(yintercept = 1) +
  labs(y = "ARI Ratio", x = "") + 
  theme_classic(base_size = 14)
```

``` {r Partition comparison: session similarity matrices (Fig. 10), fig.align="center", out.width = "60%", fig.cap = "Similarity matrices showing pattern agreement across sessions for the whole brain (left), and for PCC and mPFC separately (right), for the same 10 example subjects. The general pattern from the daily analysis is preserved, with marked individuality for mPFC and PCC, but higher for the former.", echo=FALSE, message = FALSE}
# plot
par(mfrow=c(1,2))
corrplot(RI_all_between_sess_plot, 
         is.corr = F, 
         method = "color", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(-0.03,1),
         cl.pos = "n",
         cl.length = 3,
         mar = c(1.1,1.1,1.1,1.1), 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,40.5, lwd = 2)
# segments(0.5,0.5,40.5,0.5, lwd = 2)
# segments(0.5,40.5,40.5,40.5, lwd = 2)
# segments(40.5,0.5,40.5,40.5, lwd = 2)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("Subjects (Session)")), side = 2, line = 3)
corrplot(RI_PCC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "lower", 
         tl.pos = "n", 
         tl.cex = 0.5,
         tl.col = "black", 
         #cl.lim = c(0,1),
         cl.length = 3,
         cl.pos = "r", 
         addgrid.col = "grey90")
# segments(0.5,0.5,0.5,20.5, lwd = 2)
# segments(0.5,0.5,20.5,0.5, lwd = 2)
# segments(0.5,20.5,20.5,20.5, lwd = 2)
# segments(20.5,0.5,20.5,20.5, lwd = 2)
corrplot(RI_PFC_sess_plot, 
         is.corr = F, 
         method = "color", 
         type = "upper", 
         tl.pos = "n", 
         tl.col = "black", 
         cl.pos = "n", 
         addgrid.col = "grey90",
         add = T)
mtext(expression(bold("Subjects (Session)")), line = 1)
mtext(expression(bold("mPFC")), line = 0, at = par("usr")[1]+0.8*diff(par("usr")[1:2]), col = "steelblue4")
mtext(expression(bold("PCC")), side = 1, line = 1, at = par("usr")[1]+0.09*diff(par("usr")[1:2]), col = "steelblue4")
```

``` {r Partition comparison: session ratios (Fig. 11), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Whole group ratio between within- and between-subject ARI for mPFC and PCC based on sessions. Consistent with the daily analysis, both regions show idiosyncrasy, with mPFC being significantly more subject-specific.", echo=FALSE, message = FALSE}
ggplot(data = Sess_RIRatios_summary, aes(Region, RI, fill = Region)) + 
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) + 
  ylim(0, NA) +
  geom_hline(yintercept = 1) +
  labs(y = "ARI Ratio", x = "") + 
  theme_classic(base_size = 14)
```

``` {r Noise Effects: tSNR Comparison (Fig. 12), fig.align="center", fig.width=3, fig.height=3, fig.cap = "WEIRD: Mean tSNR for mPFC and PCC across participants. This measure was derived from the minimally preprocessed fMRI data from the HCP, and thus shows the base level of reltive noise in each region.", echo=FALSE, message = FALSE}
# Plot the mPFC SNR vs PCC SNR for each subject (one figure containing all subjects)
snrmeanComp_plot <- ggplot(data = SNR_meanComp$Values, aes(Region, SNR, fill = Region)) +
  geom_boxplot(show.legend = F) +
  scale_fill_manual(values = Cols[seq(2)]) +
  labs(x = "", y = "tSNR") +
  theme(text = element_text(size=35)) +
  theme_classic()
snrmeanComp_plot
```

<!--
``` {r Noise Effects: Mean R-sqd mPFC and PCC (Fig. 13), fig.align="center", fig.width=6, fig.height=4, fig.cap = "Differences in mean R-squared values for each region per participant. The figure shows that PCC vertices tend to be more coupled with the overall dynamics of DMN across subjects.", echo=FALSE, message = FALSE}
#v4
```
-->

``` {r Noise Effects: R-sqd vs tSNR (Fig. 13), fig.align="center", fig.width=5, fig.height=3, fig.cap = "Vertex tSNR values across all subjects are correlated with their position along the z-axis, with vmPFC showing the lowest tSNR (left). However, R-square values do not show this strong relationship (right), suggesting that the coupling of each vertex is not necessarily influenced by signal noise.", echo=FALSE, message = FALSE}
# grid.arrange(v6, v7, ncol = 2)
# par(mfrow = c(1,2))
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$Rsquared, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "R-squared Value",
#               ylab = "Z-Coordinate")
# 
# smoothScatter(allVariance[allVariance$Region == "mPFC",]$varCoeff, allVariance[allVariance$Region == "mPFC",]$tempZ,
#               xlab = "Coefficient of Variation (SNR)",
#               ylab = "")

@@

``` {r Correlation vs community detection: comparison plot (Fig. 15), fig.align="center", fig.width=3, fig.height=3, fig.cap = "Day 1 vs Day 2 correlation coefficients for every method, as well as between methods. Community detection through spectral partitioning provides the most stable inter-day estimates, even though both methods show good level of agreement.", echo=FALSE, message = FALSE}
# Day 1 vs Day 2 Spatial Correlation Comparison
prepostComp_plot <- ggplot(data = prepostComp, aes(Approach, Correlation, fill = Approach)) +
  geom_boxplot(show.legend = F) +
  labs(x = "", y = "Correlation Coefficient") +
  ylim(0,1) +
  theme(text = element_text(size=35)) +
  theme_classic()
prepostComp_plot

@@

```{r BandB comparison (Figure 16), out.width = "100%", fig.align = "center", fig.cap= "Qualitative comparison between maps produced by seed-based connectivity based on Braga and Buckner's (2017) criterion, and those produced by spectral partitioning. Networks A and B were produced by carefully selecting a DLPFC seed (pointed by the green arrows). In each case, our DMN and non-DMN networks map remarkably well to their proposed functional organization."}

# Change to inflated eventually
include_graphics("./Images/braga_comparison.png")
